---
title: "Homework 1"
author: Xiangyi Liu
output: github_document
---

This is my Homework 1 solution. 

```{r,message=FALSE}
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
```

# Problem 1
###### Create a data frame comprised of specific varible types.

```{r}
prob1_df=
  tibble(
  samp=rnorm(10),
  samp_gt_0=samp > 0,
  char_vec=c("a","b","c","d","e","f","g","h","i","j"),
  factor_vec=factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)
```
###### Take the mean of each variable in my data frame.

```{r mean pull var, collapse=TRUE}
mean(pull(prob1_df,samp))
mean(pull(prob1_df,samp_gt_0))
mean(pull(prob1_df,char_vec))
mean(pull(prob1_df,factor_vec))
```
I can take the mean of numbers and logical but not character or factor. 

###### Convert variable types.
```{r convert to numeric,collapse=TRUE,results='hide'}
as.numeric(pull(prob1_df,samp_gt_0))
as.numeric(pull(prob1_df,char_vec))
as.numeric(pull(prob1_df,factor_vec))
```
NAs are introduced when coverting the character vector to numeric

```{r more conversion,collapse=TRUE}
as.numeric(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
as.factor(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
as.numeric(as.factor(pull(prob1_df,samp_gt_0)))*pull(prob1_df,samp)
```


# Problem 2

```{r,message=FALSE}
data("penguins", package = "palmerpenguins")
```

* __Dimension__: The _penguins_ dataset consists of `r nrow(penguins)` rows and `r ncol(penguins)` columns. Variables include _`r names(penguins)`_. 
* __Variables__:  _species_, _island_ , _sex_, and _year_ are factors. The other variables are numeric.
 
* _species_
    + {`r unique(pull(penguins, species))`}
* _island_
    + {`r unique(pull(penguins, island))`}
* _sex_
    + {`r unique(pull(penguins, sex))`}
* _year_
    + {`r unique(pull(penguins, year))`}
    
* _bill_length_mm_
    + Range: `r min(pull(penguins, bill_length_mm),na.rm=T)`~`r max(pull(penguins, bill_length_mm),na.rm=T)`
    + Mean: `r format(round(mean(pull(penguins, bill_length_mm),na.rm=T),2),nsmall=T)`
    + Median: `r median(pull(penguins, bill_length_mm),na.rm=T)`
    + Number of NAs: `r sum(is.na(pull(penguins, bill_length_mm)))`

* _bill_depth_mm_
    + Range: `r min(pull(penguins, bill_depth_mm),na.rm=T)`~`r max(pull(penguins, bill_depth_mm),na.rm=T)`
    + Mean: `r format(round(mean(pull(penguins, bill_depth_mm),na.rm=T),2),nsmall=T)`
    + Median: `r median(pull(penguins, bill_depth_mm),na.rm=T)`
    + Number of NAs: `r sum(is.na(pull(penguins, bill_depth_mm)))`

* _flipper_length_mm_
    + Range: `r min(pull(penguins, flipper_length_mm),na.rm=T)`~`r max(pull(penguins, flipper_length_mm),na.rm=T)`
    + Mean: `r format(round(mean(pull(penguins, flipper_length_mm),na.rm=T),2),nsmall=T)`
    + Median: `r median(pull(penguins, flipper_length_mm),na.rm=T)`
    + Number of NAs: `r sum(is.na(pull(penguins, flipper_length_mm)))`

* _body_mass_g_
    + Range: `r min(pull(penguins, body_mass_g),na.rm=T)`~`r max(pull(penguins, body_mass_g),na.rm=T)`
    + Mean: `r format(round(mean(pull(penguins, body_mass_g),na.rm=T),2),nsmall=T)`
    + Median: `r median(pull(penguins, body_mass_g),na.rm=T)`
    + Number of NAs: `r sum(is.na(pull(penguins, body_mass_g)))`




The mean of flipper length is `r format(round(mean(pull(penguins, flipper_length_mm),na.rm=T),2),nsmall=2)`mm.

###### ScatterPlot
```{r scatterplot,warning=FALSE,message=FALSE}
ggplot(penguins,aes(x=bill_length_mm,y=flipper_length_mm))+geom_point(aes(color=species))
ggsave("penguins_plot.pdf")
```                                                                      
                                                                    



